\mytitle

### 2012-03-13 papers/SAS2012/implicitization.tex
positionnement des floats

\begin{figure}
\label{fig:example-graph}
\begin{minipage}[c]{.15\textwidth}
\begin{tikzpicture}[->,>=stealth',auto,node distance=2.5cm,
                    semithick,font=\footnotesize]

@@

  \path [transition] 
		(n00) edge  node {$\lstinline|x_old| \gets 0$} (n0);
  \path [transition] 
		(n0) edge  [loop left] node [left, xshift=0.2cm] {
		$\begin{array}{r}
			-10000 \leq \lstinline|x| \leq 10000 \\
			\lstinline|x_old|-10 \leq \lstinline|x| \leq \lstinline|x_old|+10 /\\
			\lstinline|x_old| \gets \lstinline|x|
		\end{array}$
		} (n0);
  \path [transition] 
		(n0) edge node [left, yshift=-0.2cm, xshift=0] {
		$\begin{array}{r}
			-10000 \leq \lstinline|x| \leq 10000 \\
			\lstinline|x_old|-10 \leq \lstinline|x| \leq \lstinline|x_old|+10 /\\
			\lstinline|x_old| \gets \lstinline|x|
		\end{array}$
		} (n1);
\end{tikzpicture}
\end{minipage}
\caption{Ascending sequence of subgraphs}
\end{figure}

@@

We conducted extensive experiments on real-life programs in order to compare the
different techniques, mostly on open-source projects (Fig.~\ref{fig:projects}) written in C, C++ and Fortran.
\MM{TODO: résumer les conclusions sur les résultats}

\begin{figure}[h!]
      \centering
      \begin{tabular}{|l|r|r|r|r|r|r|r|} \hline
        \multicolumn{1}{|c|}{} &
        \multicolumn{2}{c|}{Size} &
        \multicolumn{5}{c|}{Execution time (seconds)} \\ \hline
        \multicolumn{1}{|c|}{Name} & 
        \multicolumn{1}{c|}{kLOC}  & 
        \multicolumn{1}{c|}{$|P_R|$}  &
        \multicolumn{1}{c|}{\textbf{S}} &
        \multicolumn{1}{c|}{\textbf{G}} &
        \multicolumn{1}{c|}{\textbf{PF}} &
        \multicolumn{1}{c|}{\textbf{G+PF}} &
	\multicolumn{1}{c|}{\textbf{DIS}} \\ 
        \hline
        % M-x align RET powers ;-).
		\input{table_time}
	\hline
      \end{tabular}
      \label{fig:projects}

    \input{gnuplot/techniques.tex}
  \vspace{-20pt}
  \caption{Comparison of the abstract values obtained on several open-source projects. The table shows
  their respective number of lines of code, number of control points in $P_R$, and execution time
  on various techniques.
  Techniques are classical abstract
  interpretation (S), \emph{Guided Static
  Analysis} (G), \emph{Path-focused} technique (PF), our combined technique
  (G+PF), and its version with disjunctive invariants (DIS).
  The $\subsetneq$ bars gives the percentage of invariants stronger (more precise; smaller with respect to inclusion) with the left-side technique,
$\supsetneq$ the percentage of invariants stronger with the right-side technique,
and ``uncomparable'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller;
the code points where both invariants are equal make up the remaining percentage. See Tab.~\ref{tab:techniques} for details.}
  \label{fig:techniques}
\end {figure}

\MM{Bon, c'est vraiment frustrant de se limiter à ça, mais pour écrire
  plus, faut trouver de la place}
These results confirm that our combined technique improve the
analysis in comparison with the two techniques taken individually, at
a reasonable cost. The extension with disjunctive invariants increases
precision in many cases, but with higher cost in terms of execution
time.

@@

>>>>

\begin{figure}
\begin{minipage}[c]{.15\textwidth}
\begin{tikzpicture}[->,>=stealth',auto,node distance=2.5cm,
                    semithick,font=\footnotesize]

@@

  \path [transition] 
		(n00) edge  node {$\lstinline|x_old| \gets 0$} (n0);
  \path [transition] 
		(n0) edge  [loop left] node [left, xshift=0.2cm] {
		$\begin{array}{r}
			-10000 \leq \lstinline|x| \leq 10000 \\
			\lstinline|x_old|-10 \leq \lstinline|x| \leq \lstinline|x_old|+10 /\\
			\lstinline|x_old| \gets \lstinline|x|
		\end{array}$
		} (n0);
  \path [transition] 
		(n0) edge node [left, yshift=-0.2cm, xshift=0] {
		$\begin{array}{r}
			-10000 \leq \lstinline|x| \leq 10000 \\
			\lstinline|x_old|-10 \leq \lstinline|x| \leq \lstinline|x_old|+10 /\\
			\lstinline|x_old| \gets \lstinline|x|
		\end{array}$
		} (n1);
\end{tikzpicture}
\end{minipage}
\caption{Ascending sequence of subgraphs}
\label{fig:example-graph}
\end{figure}

@@

We conducted extensive experiments on real-life programs in order to compare the
different techniques, mostly on open-source projects (Fig.~\ref{fig:projects}) written in C, C++ and Fortran.
These results confirm that our combined technique improve the
analysis in comparison with the two techniques taken individually, at
a reasonable cost. The extension with disjunctive invariants increases
precision in many cases, but with higher cost in terms of execution
time.

\MM{TODO: résumer les conclusions sur les résultats}

@@

\begin{table}[h!]\centering
      \begin{tabular}{|l|r|r|r|r|r|r|r|} \hline
        \multicolumn{1}{|c|}{} &
        \multicolumn{2}{c|}{Size} &
        \multicolumn{5}{c|}{Execution time (seconds)} \\ \hline
        \multicolumn{1}{|c|}{Name} & 
        \multicolumn{1}{c|}{kLOC}  & 
        \multicolumn{1}{c|}{$|P_R|$}  &
        \multicolumn{1}{c|}{\textbf{S}} &
        \multicolumn{1}{c|}{\textbf{G}} &
        \multicolumn{1}{c|}{\textbf{PF}} &
        \multicolumn{1}{c|}{\textbf{G+PF}} &
	\multicolumn{1}{c|}{\textbf{DIS}} \\ 
        \hline
        % M-x align RET powers ;-).
		\input{table_time}
	\hline
      \end{tabular}
\caption{Execution times for various techniques}
\label{tab:time}
\end{table}

\begin{figure}[h!]%
      \centering%
    \input{gnuplot/techniques.tex}
  \vspace{-20pt}
  \caption{Comparison of the abstract values obtained on several open-source projects. The table shows
  their respective number of lines of code, number of control points in $P_R$, and execution time
  on various techniques.
  Techniques are classical abstract
  interpretation (S), \emph{Guided Static
  Analysis} (G), \emph{Path-focused} technique (PF), our combined technique
  (G+PF), and its version with disjunctive invariants (DIS).
  The $\subsetneq$ bars (resp. $\supsetneq$) gives the percentage of invariants stronger (more precise; smaller with respect to inclusion) with the left-side (resp. right-side) technique,
and ``uncomparable'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller;
the code points where both invariants are equal make up the remaining percentage. See Tab.~\ref{tab:techniques} for details.}
  \label{fig:techniques}
  \label{fig:projects}
\end {figure}

\MM{Bon, c'est vraiment frustrant de se limiter à ça, mais pour écrire
  plus, faut trouver de la place}
